Interactive Visual Analysis of Image-Centric Cohort Study Data

### 2014-06-21 draft.tex
Started Work on Related Work

% - Missing Data\\
% - Follow-Up Questions?\\
% - grouping essential\\
% - problems when analyzing image data\\
% 	- what are Problems there\\
% 	- how can shape be included?\\
% 	- show image data of multiple subjects
% ---------------------------------------------------------------------------------
% ----------------------------------- Section -------------------------------------
% ---------------------------------------------------------------------------------
\section{Prior and Related Work}
%Designing a visualization, which conveys all data aspects equally, is challenging.
%
Given the number of features of epidemiological data sets and their different manifestations, the strength of different visualization techniques needs to be combined \cite{Buja91, Konyha2009}.
%
The principal component analysis (PCA) and similar techniques are able to reduce the dimensions by extracting most expressive components, but make the influence of each variable hard to convey.
\\\\
%Their focus on \emph{hypothesis generation} using parallel assessment of multiple data features makes the work of Turkay and colleagues closest to ours albeit our emphasis on processing models derived from medical image data segmentation and variables with categorical manifestations \cite{Turkay2013}.
\rem{Their} \add{Turkay and colleagues \cite{Turkay2013}} focus on \emph{hypothesis generation} using parallel assessment of multiple data features makes \rem{the work of Turkay and colleagues} \add{their work} closest to ours albeit our emphasis is on processing models derived from medical image data segmentation and variables with categorical manifestations \rem{\cite{Turkay2013}}.
%
Their methods aim to amplify a hypothesis generation process for analyzing data of a Norwegian aging study.
%
Statistical measures of continuous features, such as mean, standard deviation, skewness, or inter-quartile range, are used to create \emph{dimension plots}. %that make them comparable with respect to the derived descriptive measures, such as voxel number of a segmented structure.
%
These transform dimensions into data points and make them comparable with respect to the derived descriptive measures, making them comparable.
%
%This not only allows for comparing all continuous variables in a single plot but make their distribution change comprehensible.
%
%This requires a good descriptive measure which captures the kind of change the user is interested in or which reflects unexpected data behavior.
%
%The technique was applied to features obtained by segmenting the brain into 45 parts and measure the voxel number, volume and properties of the intensity values.
%
The method is strongly dependent on the descriptive measures of the epidemiological factors.

>>>>

% - Missing Data\\
% - Follow-Up Questions?\\
% - grouping essential\\
% - problems when analyzing image data\\
% 	- what are Problems there\\
% 	- how can shape be included?\\
% 	- show image data of multiple subjects
% ---------------------------------------------------------------------------------
% ----------------------------------- Section -------------------------------------
% ---------------------------------------------------------------------------------
\section{Prior and Related Work}
\com{\textbf{Reviewer 1}: The related work section includes merely a set of related tools. I would have liked to see a more comprehensive section that discusses the previous related work in more detail and describes why they are important and relevant to this work and how your work differs or improves upon theirs.\\
%
Quality: The work contains many references. But there are potentially some missing; e.g, the framework talks about utilizing multiple coordinated views (although the details of what is actually linked is vague) and therefore cited papers such as Baldonado's work in AVI 2000, or Roberts 2007 on Coordinated multiple views, or Weaver's Cross-filtered Views for multidimensional visual analysis 2010 should be cited. The paper really proposes a framework; however it was unclear how this was implemented into the presented system. Therefore this should be improved.\\\\
%
\textbf{Reviewer 2}
- I would suggest to also cite the original Generalized Pairs Plot and 
not only the adaptation as GPLOMS [21]: J. W. Emerson and W. A. Green. 
gpairs: The Generalized Pairs Plot, 2012. R package version 1.1.\\
%
- A related process model for Visual Analytics that focuses on hypotheses 
and models: T. Lammarsch, W. Aigner, A. Bertone, S. Miksch, and A. Rind, 
“Towards a Concept how the Structure of Time can Support the Visual 
Analytics Process,” in Proceedings of International Workshop on Visual 
Analytics (EuroVA 2011) in conjunction with EuroVis 2011, Goslar, 
Germany, 2011, pp. 9–12.\\
%
- VISITORS is related work in visualization of medical variables of 
cohorts: D. Klimov, Y. Shahar, and M. Taieb-Maimon, “Intelligent 
visualization and exploration of time-oriented data of multiple 
patients,” Artificial Intelligence in Medicine, vol. 49, no. 1, pp. 
11–31, May 2010.\\
%
- another, forthcoming related paper: P. Angelelli, S. Oeltze, C. Turkay, 
J. Haasz, E. Hodneland, A. Lundervold, A. Lundervold, B. Preim, and H. 
Hauser, “Interactive Visual Analysis of Heterogeneous Cohort Study 
Data,” IEEE Computer Graphics and Applications, vol. Early Access 
Online, 2014.\\\\
%
\textbf{Reviewer 3}
What the prior work section needs at the end is a paragraph stating how their work differs from the work they summarise i.e. it uses more non-image data than Turkay and uses different visualisations, and more importantly differentiation from Steenwijk et al’s very similar work (saying they use a different meaning for the word “cohort” does not seem justification enough, given the large overlap), only then can we be sure there is a novel contribution here.}
%Designing a visualization, which conveys all data aspects equally, is challenging.
%
Given the number of features of epidemiological data sets and their different manifestations, the strength of different visualization techniques needs to be combined \cite{Buja91, Konyha2009}.
%
The principal component analysis (PCA) and similar techniques are able to reduce the dimensions by extracting most expressive components, but make the influence of each variable hard to convey.
\\\\
%Their focus on \emph{hypothesis generation} using parallel assessment of multiple data features makes the work of Turkay and colleagues closest to ours albeit our emphasis on processing models derived from medical image data segmentation and variables with categorical manifestations \cite{Turkay2013}.
\rem{Their} \add{Turkay and colleagues \cite{Turkay2013}} focus on \emph{hypothesis generation} using parallel assessment of multiple data features makes \rem{the work of Turkay and colleagues} \add{their work} closest to ours albeit our emphasis is on processing models derived from medical image data segmentation and variables with categorical manifestations \rem{\cite{Turkay2013}}.
%
Their methods aim to amplify a hypothesis generation process for analyzing data of a Norwegian aging study.
%
Statistical measures of continuous features, such as mean, standard deviation, skewness, or inter-quartile range, are used to create \emph{dimension plots}. %that make them comparable with respect to the derived descriptive measures, such as voxel number of a segmented structure.
%
These transform dimensions into data points and make them comparable with respect to the derived descriptive measures, making them comparable.
%
%This not only allows for comparing all continuous variables in a single plot but make their distribution change comprehensible.
%
%This requires a good descriptive measure which captures the kind of change the user is interested in or which reflects unexpected data behavior.
%
%The technique was applied to features obtained by segmenting the brain into 45 parts and measure the voxel number, volume and properties of the intensity values.
%
The method is strongly dependent on the descriptive measures of the epidemiological factors.
